### 2015-02-02 cav-2015-tex/summary-heap.tex
Finished crunch on math

\section{Summary Heap Framework}
The summary heap algorithm is defined using
Javalite~\cite{saints-MS}. The small-step semantics of Javalite,
defined as a syntactic machine using a CESK architecture, are modified
to perform symbolic execution on a summary heap. The surface (input)
and machine (state) syntax is shown
in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
are italicized. Ellipses indicate zero or more repetitions. Tuples
omit the commas for compactness.

@@

\begin{comment}
MOVE TO THE PROOF SECTION
To show the heap summary algorithm is sound and complete with respect
to properties proved by GSE, a transition relation that
relates states according GSE is defined as $\rgse$ or $p \rgse
p^\prime$. Similarly the transition relation for the new summary heap algorithm is given as
$\rsym$ or $q \rsym q^\prime$ (defined in the next section). For simplicity, both use lazy
initialization as opposed to lazier or lazier\#. The full operational semantics for $\rgse$ are in the appendix. 
\end{comment}

>>>>

\section{Summary Heap Framework}
\label{sec:sh}
The summary heap algorithm is defined using
Javalite~\cite{saints-MS}. The small-step semantics of Javalite,
defined as a syntactic machine using a CESK architecture, are modified
to perform symbolic execution on a summary heap. The surface (input)
and machine (state) syntax is shown
in~\figref{fig:syntax}. Terminals are in bold face while non-terminals
are italicized. Ellipses indicate zero or more repetitions. Tuples
omit the commas for compactness.

@@
